---
title: "R Notebook"
output: html_notebook
---


Q2) Loading packages
```{r}
library(tidyverse)
library(ggthemes)
```

Q3) Importing data

```{r}
assignment4 = read_csv("assignment4.csv")
```

Q4) Rows and columns
```{r}
nrow(assignment4) 
ncol(assignment4)
```
There are 3700 rows and 12 columns in this data file.

Q5) Unique participants & trials 
```{r}

num_subjects = 
assignment4 %>% 
  pull(subject)

unique_subjects = unique(num_subjects)

trial_groups = 
assignment4 %>%
  group_by(trial)

num_trials = count(trial_groups)
```
There are 37 unique subjects and each subject completed 100 trials.

Q6) Levels of variables 
```{r}
prime_conditions = 
assignment4 %>% 
  pull(prime_condition)

lev_prime = levels(prime_conditions) <- c("both", "semantic", "unrelated","phonological") 

states = 
assignment4 %>% 
  pull(state)

lev_state= levels(states) <- c("know", "dontknow", "tipoftongue","other") 


```
The prime condition has four levels and the state condition has four levels.

Q7) Subsets of columns
```{r}
prime_information = 
  assignment4 %>% 
  select(subject, prime_condition)
```

Q8) Subsets of rows
```{r}
phonological = 
   assignment4 %>%
   filter(prime_condition == "phonological" & accuracy == "1")
```

Q9) Summarizing accuracy per subject 
```{r}
subject_acc = 
  assignment4 %>% 
  group_by(subject) %>%
  summarise(subject_id = mean(accuracy))
```

Q10) Summarizing accuracy per prime condition 
```{r}
prime_acc = assignment4 %>% 
  group_by(prime_condition) %>%
  summarise(mean_acc = mean(accuracy),sd_acc = sd(accuracy))
```

Q11) Histogram of subject accuracy 
```{r}
subject_acc %>% 
  ggplot(aes(x = subject_id)) +
  geom_histogram(binwidth = 0.2, 
                 fill = "red", 
                 color = "black", 
                 position = "identity") + 
  theme_few() +
  xlab("Mean Accuracy") + ylab ("Count") + ggtitle("Histogram of Mean Accuracy")
```

Q12) Bar plot of prime condition 
```{r}
prime_acc %>% 
  ggplot(aes(x = prime_condition, y = mean_acc)) +
  geom_bar(stat = "identity",
           fill = "blue", 
           color = "black") + 
  theme_few() +
  xlab("Prime Condition") + ylab ("Mean Accuracy") + ggtitle("Mean Accuracy Across Prime Condition")
```

Q13) Data interpretation 

It appears that type of prime influences accuracy. Accuracy is highest in the
phonological prime condition and lowest in the semantic prime conditions. 
Unrelated and both primes result in similar accuracy between the other two.

Q14) Summarizing accuracy per prime condition and state 
```{r}
state_prime_acc = 
  assignment4 %>% 
  group_by(prime_condition, state) %>%
  summarise(mean_acc = mean(accuracy))
```

Q15) Bar plot of prime condition and state 
```{r}
state_prime_acc %>% 
  ggplot(aes(x = prime_condition, y = mean_acc, fill = state)) +
  geom_bar(stat = "identity",
           position = "dodge") +
  theme_few() +
  xlab("Prime Condition") + ylab ("Mean Accuracy") + ggtitle("Mean Accuracy Across Prime Condition and Reported States")
```
